Minimal trap-spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-02 cmsb22.tex
Refer to some places (not fully provided now) where people can access the real-world models to reproduce the benchmark. We can also put all the model files into the Git repo.

\begin{table}[!ht]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the selected real-world models.
    Columns "\(n\)", "\(e\)", and "\(s\)" denote the numbers of nodes, interactions, and source nodes of each model, respectively.
    Column "\(|M|\)" denotes the number of minimal trap spaces.
    The computation times are all in seconds.
    "DNF" means that the method did not finish the computation within one hour.}
  \label{tab:result_real}
  \begin{tabular}{lrrrrrrrrr}
    \toprule
    & & & & & & \multicolumn{2}{c}{PyBoolNet} & \multicolumn{2}{c}{Proposed method}\\
    \cmidrule(lr){7-8}\cmidrule(lr){9-10}
    model & $n$ & $e$ & $s$ & $|M|$ & $|F|$ & t1 (s) & t2 (s) & t1 (s) & t2 (s) \\ \midrule
    CASCADE-3 & 183 & - & 0 & 1 & 0 & - & - & 1.65 & - \\
    CHO-2016 & 200 & - & 13 & 1024 & 0 & - & - & 2.10 & - \\
    CACC & 70 & 153 & 1 & 10 & 2 & - & - & 0.18 & - \\
    THIL\_17 & 92 & - & 16 & 5724 & 5724 & - & - & 0.90 & - \\
    ERBB & 247 & 1100 & 22 & 1456394+ & 0 & DNF & DNF & DNF & - \\
    ER-STRESS & 182 & 266 & 75 & 25600 & 25600 & - & - & 4.54 & - \\
    AD & 1169 & - & 469 & 49152 & 49152 & - & - & 66.17 & - \\
    Cholocystokinin & 404 & - & 95 & 705024 & 705024 & - & - & 1080.35 & - \\
    FIBROBLASTS & 139 & 557 & 9 & 375850 & 32768 & - & - & 331.87 & - \\
    TcellCheckPoint & 218 & - & 34 & 15360 & 10240 & - & - & 4.33 & - \\
    HIV-1 & 138 & 368 & 14 & 1408 & 1408 & DNF & DNF & 1.44 & - \\
    HMOX1 & 145 & 228 & 56 & 5120 & 5120 & - & - & 0.99 & - \\
    Human network & 1953 & - & 675 & 2048 & 2048 & DNF & DNF & 1770.98 & - \\
    IL\_6 Signalling & 86 & 149 & 15 & 512 & 448 & - & - & 0.32 & - \\
    IMMUNE-SYS & 164 & 506 & 13 & 36852 & 27871 & DNF & DNF & 14.19 & - \\
    IBD & 47 & 287 & 0 & 1 & 0 & DNF & DNF & 296.23 & - \\
    Influenza A & 131 & 302 & 11 & 2560 & 2560 & - & - & 1.07 & - \\
    INTERFERON-1 & 121 & 190 & 55 & 512 & 512 & - & - & 0.43 & - \\
    KORKUT-2015 & 99 & - & 12 & 2060 & 1384 & DNF & DNF & 2.86 & - \\
    KY-PA & 150 & 304 & 72 & 512 & 512 & - & - & 3.79 & - \\
    RA Apoptosis & 431 & - & 59 & 640 & 0 & DNF & DNF & 0.70 & - \\
    CELL CYCLE 2020 & 121 & 493 & - & 78 & 78 & - & - & 3.72 & - \\
    S1\_Table & 1659 & - & 522 & 1024 & 1024 & DNF & DNF & 1511.07 & - \\
    Macrophage\_Act & 321 & 533 & 19 & 512 & 384 & - & - & 1.58 & - \\
    SIPC & 133 & 431 & 0 & 812 & 746 & - & - & 1.40 & - \\
    SPBP & 66 & 139 & 13 & 512 & 256 & - & - & 0.17 & - \\
    SN5 & 2746 & - & 835 & 2048 & 2048 & DNF & DNF & 3094.04 & - \\
    TCR-TLR5-SIG & 130 & 273 & 2 & 48 & 48 & - & - & 0.50 & - \\
    TLGLSurvival & 61 & 193 & 7 & 318 & 172 & - & - & 0.24 & - \\
    TUREI-2016 & 4691 & - & 1257 & - & - & DNF & DNF & DNF & DNF \\
    VIRUS-RE-CYC & 154 & 268 & 25 & 1024 & 1024 & - & - & 0.67 & - \\ \bottomrule
  \end{tabular}

>>>>

\begin{table}[!ht]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the selected real-world models.
    Columns "\(n\)", "\(e\)", and "\(s\)" denote the numbers of nodes, interactions, and source nodes of each model, respectively.
    Column "\(|M|\)" denotes the number of minimal trap spaces.
    The computation times are all in seconds.
    "DNF" means that the method did not finish the computation within one hour.}
  \label{tab:result_real}
  \begin{tabular}{lrrrrrrrrr}
    \toprule
    & & & & & & \multicolumn{2}{c}{PyBoolNet} & \multicolumn{2}{c}{Proposed method}\\
    \cmidrule(lr){7-8}\cmidrule(lr){9-10}
    model & $n$ & $e$ & $s$ & $|M|$ & $|F|$ & t1 (s) & t2 (s) & t1 (s) & t2 (s) \\ \midrule
    CASCADE-3~\cite{Tsirvouli2020} & 183 & - & 0 & 1 & 0 & - & - & 1.65 & - \\
    CHO-2016 & 200 & - & 13 & 1024 & 0 & - & - & 2.10 & - \\
    CACC~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 70 & 153 & 1 & 10 & 2 & - & - & 0.18 & - \\
    THIL\_17 & 92 & - & 16 & 5724 & 5724 & - & - & 0.90 & - \\
    ERBB & 247 & 1100 & 22 & 1456394+ & 0 & DNF & DNF & DNF & - \\
    ER-STRESS & 182 & 266 & 75 & 25600 & 25600 & - & - & 4.54 & - \\
    AD~\cite{aghamiri2020automated} & 1169 & - & 469 & 49152 & 49152 & - & - & 66.17 & - \\
    Cholocystokinin~\cite{aghamiri2020automated} & 404 & - & 95 & 705024 & 705024 & - & - & 1080.35 & - \\
    FIBROBLASTS~\cite{helikar2008emergent} & 139 & 557 & 9 & 375850 & 32768 & - & - & 331.87 & - \\
    TcellCheckPoint & 218 & - & 34 & 15360 & 10240 & - & - & 4.33 & - \\
    HIV-1~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 138 & 368 & 14 & 1408 & 1408 & DNF & DNF & 1.44 & - \\
    HMOX1~\cite{ostaszewski2021covid19} & 145 & 228 & 56 & 5120 & 5120 & - & - & 0.99 & - \\
    Human network & 1953 & - & 675 & 2048 & 2048 & DNF & DNF & 1770.98 & - \\
    IL\_6 Signalling~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 86 & 149 & 15 & 512 & 448 & - & - & 0.32 & - \\
    IMMUNE-SYS & 164 & 506 & 13 & 36852 & 27871 & DNF & DNF & 14.19 & - \\
    IBD~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 47 & 287 & 0 & 1 & 0 & DNF & DNF & 296.23 & - \\
    Influenza A~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 131 & 302 & 11 & 2560 & 2560 & - & - & 1.07 & - \\
    INTERFERON-1~\cite{ostaszewski2021covid19} & 121 & 190 & 55 & 512 & 512 & - & - & 0.43 & - \\
    KORKUT-2015 & 99 & - & 12 & 2060 & 1384 & DNF & DNF & 2.86 & - \\
    KY-PA & 150 & 304 & 72 & 512 & 512 & - & - & 3.79 & - \\
    RA Apoptosis~\cite{aghamiri2020automated} & 431 & - & 59 & 640 & 0 & DNF & DNF & 0.70 & - \\
    CELL CYCLE 2020 & 121 & 493 & - & 78 & 78 & - & - & 3.72 & - \\
    S1\_Table & 1659 & - & 522 & 1024 & 1024 & DNF & DNF & 1511.07 & - \\
    Macrophage\_Act~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 321 & 533 & 19 & 512 & 384 & - & - & 1.58 & - \\
    SIPC~\cite{Montagud2021} & 133 & 431 & 0 & 812 & 746 & - & - & 1.40 & - \\
    SPBP & 66 & 139 & 13 & 512 & 256 & - & - & 0.17 & - \\
    SN5~\cite{kim2013rmod} & 2746 & - & 835 & 2048 & 2048 & DNF & DNF & 3094.04 & - \\
    TCR-TLR5-SIG & 130 & 273 & 2 & 48 & 48 & - & - & 0.50 & - \\
    TLGLSurvival~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 61 & 193 & 7 & 318 & 172 & - & - & 0.24 & - \\
    TUREI-2016 & 4691 & - & 1257 & - & - & DNF & DNF & DNF & DNF \\
    VIRUS-RE-CYC & 154 & 268 & 25 & 1024 & 1024 & - & - & 0.67 & - \\ \bottomrule
  \end{tabular}
